---
title: "Lab 06 - Conveying the right message through visualisation"
author: [TEAM NAME]
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(lubridate)
```


### Exercise 1

```{r create-data}
Covid_cases <- tribble(
  ~Date, ~Masks, ~No_Masks,
  "13/7/2020", 23, 9.5,
  "14/7/2020", 19.5, 9,
  "15/7/2020", 20, 9,
  "16/7/2020", 20, 9.8,
  "17/7/2020", 20, 9.7,
  "18/7/2020", 20, 9.5,
  "19/7/2020", 20, 9.3,
  "20/7/2020", 20.5, 8.7,
  "21/7/2020", 21, 8.5,
  "22/7/2020", 20.5, 8.5,
  "23/7/2020", 20, 8.5,
  "24/7/2020", 20, 9,
  "25/7/2020", 20, 9.9,
  "26/7/2020", 19.5, 10,
  "27/7/2020", 18.5, 9.5,
  "28/7/2020", 16.5, 9.4,
  "29/7/2020", 16.5, 9.4,
  "30/7/2020", 16.5, 9.7,
  "31/7/2020", 16.3, 9.5,
  "01/8/2020", 16.2, 9,
  "02/8/2020", 16, 9,
  "03/8/2020", 15.8, 9,
)
```


### Exercise 2

```{r better-viz}
Covid_cases %>%
  mutate(Date = dmy (Date)) %>%
ggplot(aes(x = Date))+
  geom_line(aes(y = Masks),
            color = "red")+
  geom_line(aes(y = No_Masks),
            color = "blue")+
  labs(y = "Cases",
       title = "Kansas COVID 7-day Rolling Average of Daily Cases",
       subtitle = "Per 100k of population; blue: no-mask counties, red: mask counties")
```


### Exercise 3

*The scale is a lot clearer to read and much easier to compare between the no mask and mask data. As well the graph is now clearly labeled which makes understanding the data quicker. As well reducing the number of dates shown illustrates the change in the data over time better. *


### Exercise 4

*Based on the data provided, it is clear that counties with a mask mandate reported higher numbers of COVID cases than those without a mask mandate.  However, this relationship may be affected by other factors, such as population density and the amount of testing being done in each county.  Counties without a mask mandate may be more likely to have a lower population density, as well as less testing, which could explain these results.*
